Recommendations For Intelligent Code Reorganization

### 2016-08-24 Manuscript.tex
Updates from ShareLaTeX

		% \title{How to Discourage Useless Refactorings}
		\title{Toward Intelligent Refactoring Recommendations}

@@

		\begin{abstract} 
			{\bf Context: } 
			Developers use bad code smells to guide refactoring.
			Yet developers, text books, tools, and researchers disagree on which bad smells are important.
			%Many bad smell detectors recommend refactoring when static code measure
			%cross some threshold boundary. 
			%%However, it is unclear at what threshold values smell-related metrics
			%should trigger code improvement or preventative maintenance.

			\noindent 
			{\bf Objective:} To evaluate the likelihood that a refactoring to address bad code smells will yield improvement in the defect-proneness of the code.

@@

			\noindent
			{\bf Conclusion: }
			Before undertaking a refactoring based on a bad smell report,
			use a tool like XTREE to check and ignore any refactorings   that  are useless; i.e. which lacks evidence
			in the historical record  that it is useful to make that change.
			Note that this use case applies to both manual refactorings proposed by developers
			as well as refactoring  conducted by automatic methods.
			This recommendation assumes that there is an historical record.
			If none exists, then the results of this paper could be use used as a guide (see our
			Table~8).

@@

	Bad smells are a widely used technique for evaluating code. While the original bad small concept was largely subjective [REF], researchers including Marinescu [REF] and others has provided formal definitions of ``bad smells'' in terms of static code attributes such size, complexity, coupling, and other metrics. Consequently, code smells are captured by popular static analysis tools such as PMD [REF], CheckStyle [REF], FindBugs [REF], and SonarQube [REF], although not always explicitly labeled as such.

	Refactoring bad smells from code is generally accepted as a recommended practice, but refactoring by definition does not change the external functionality of the system and thus may have no perceived value. For example, this paper began when a Washington-based software company shared one of their management challenges with us: their  releases are delayed by developers spending  much time removing bad smells within their code. 
	%This management team wanted some way to check if all that activity was useful. 
	Kim et al.\cite{kim2012field} surveyed developers at Microsoft and found that refactoring incurs significant cost and risks. A Google search on the terms ``refactoring cost'' yields numerous threads on StackOverlfow from developers asking how to justify refactoring and when the costs of refactoring outweight its benefits.

@@

	% In addition to tools that capture bad smells such as FindBugs and SonarQube, a multitude of tools have been proposed to support refactoring (e.g., \cite{ge2014manual,lee2013drag,foster2012witchdoctor,ge2012reconciling}). Note that these managers are {\em not} asking for better
	% automatic refactoring
	% tool support. 
	% Their human programmers are refactoring
	% code all the time, perhaps too much so.
	% Hence, the management goal
	The challenge is to encourage refactorings that result in perceivable benefits (such as reduced defect proneness or lower maintenance costs) and avoid refactorings with no demonstrable benefit and thus waste effort.

	This paper describes one approach to evaluate whether refactorings that change the structure of code are likely to have a perceivable benefit by evaluating:
	\bi
	\item If there is no evidence in the historical record that changing ``X'' is useful;
	\item Then discourage developers from doing ``X''.
	\ei
	We use data mining to generate two oracles: a {\em primary
		change oracle} and a {\em secondary verification oracle}.
	By combining these two oracles,
	we can generate and validate useful
	changes to code modules. We focus on ``bad smells'' indicated by code metrics such as size and complexity as captured in popular tools such as SonarQube [REF] and Klocwerk [REF].

@@

	When these oracles were applied to defect data from
	open source object-oriented software systems, we discovered a {\em conjunctive fallacy}
	in the bad smell literature~\cite{erni96,bender99,Shatnawi10,Alves2010,hermans15}.
	A common heuristic is to recommend refactoring of ``bad'' code
	to make it ``better'' as follows: for all static code measures that exceed some threshold, make changes such that the thresholds are no longer exceeded. That is:
	\begin{equation}\label{eq:df}
		\scriptstyle
		\begin{array}{rl}
			\mathit{bad}    & = \left(a_1 > t_1 \right) \bigvee \left(a_2 > t_2\right) \bigvee    ...                             \\
			\mathit{better} & = \neg\;\mathit{bad} = \left(a_1 \le t_1 \right) \bigwedge \left(a_2 \le t_2\right)  \bigwedge  ... 
		\end{array}
	\end{equation}
	We say that the above definition of ``better'' is a conjunctive fallacy
	since it assumes that the best way to improve code is to decreases multiple code attribute measures below $t_i$ in order
	to remove the ``bad'' smells. In reality, there exists an intricate set of associations between static code measures
	such that {\em decreasing}  $a_i$ necessitates {\em increasing} $a_j$.
	It is easy to see why this is so.
	A requirement for  refactoring is that the new code supports the same functionality
	as before. If we pull code out of a function (since that function has grown too
	large), {\em that functionality has to go somewhere else}. What we see in XTREE's change
	recommendation is that if we decrease a module's lines of code  then in the refactored
	code, the functionality is achieved via a communication between several different parts
	of the system. That is, {\em decreasing} the lines of code metric within a module {\em increases}
	that module's coupling metrics.

@@

	This paper  claims that (a)~XTREE is a  better way than \eq{df}  to define useful changes to software and (b)~those changes are useful for recognizing   superfluous refactorings since they usually refer to a very 
	small subset of the static code measures (which allows us to rule out refactorings based on any of the omitted
	static code measures). 
	In support of these claims, 
	the rest of this paper is structured as follows. In Section~2, we offer some background on bad smells. In Section~3, 
	different methods are presented for determining when code does/does not have bad smell. One of those methods
	will be XTREE while the others will come from other researchers. Section~4
	defines an assessment method that checks which of these methods is most useful. The results from that assessment 
	are presented in Section~5. Those results will answer five research questions.

@@

	{\bf RQ3: Stopping}: Our advice to managers is to discourage refactoring based on changes that lack
	historical evidence of being effective. How effective is XTREE at offering such ``stopping points'' (i.e. clear guidance on what {\em not} to do)??
	\begin{lesson}
		In  any  project,  XTREE's  recommended  changes  only  mentions one to four 
		of the  static code attributes.  Any bad smell defined in terms of the remaining 19 to 16 code attributes (i.e. most of them)
		would hence be deprecated.
	\end{lesson}

@@

	{\bf RQ5: Conjunctive Fallacy}:  
	Is it always  useful  to aplly \eq{df}; i.e. make code better by   reducing the values of  multiple code attributes? We find that:
	\begin{lesson}
		XTREE usually recommends reducing lines of code (size of the modules).
		That said,  XTREE often recommends {\em increasing} the values of other static code attributes.
	\end{lesson} 
	Note that {\bf RQ3, RQ4, RQ5} 
	confirms the intuitions
	of the project managers that prompted this investigation:
	\bi
	\item
	Yes,  indeed, their programmers
	were wasting time on   performing refactorings  that  decreased multiple measures when, in fact,
	they should be trying to {\em decrease} some measures while {\em increasing} others.
	\item
	Across all studied projects, XTREE found that  around one-fifth  
	of the measures were usually found within  change recommendations. That is, it is 80\% likely that
	that refactoring based on reducing any one measurement picked at random will be useful.
	\ei
	Consequently, we  recommend the following use case for  XTREE:
	\bi
	\item Before doing  refactoring based on a bad smell report...
	\item ...check and discourage any refactoring   for which there is no proof
	in the historical record that the change improves the code.
	\ei
	This use case described  applies to both manual refactorings proposed by developers
	as well as refactoring conducted by automatic methods~\cite{mkaouer2015many}. That is, XTREE could optimize automatic
	code refactoring by discouraging refactorings for useless goals.

	\subsection{ Threats to Validity}

	The results of this paper are biased by out choice of refactoring goal (reducing defects) and our choice
	of measures collected from software project (OO measures such as
	depth of inheritance, number of child classes, etc).

	The recommendation to management, shown on page one of this paper,  was to discourage developers doing ``X'' if there was no historical evidence that ``X'' was useful. 
	This recommendation assumes that such an  historical record can be accessed. If not,  then the results of this paper could be use used as a guide (see our Table 8). Alternatively, some form of transfer learning~\cite{Nam15,Jing15,krishna16} could be used to import data from another project (but more research would be required to test the validity of combing tools like XTREEs with transfer learning).

@@

	Much research endorses them to guide
	code improvement (e.g., refactoring or preventative maintenance). A recent literature review by Tufano et al.~\cite{Tufano2015}  
	lists dozens of papers on smell detection and repair tools. 
	Yet
	other papers cast doubt on the value of bad smells
	as triggers for code improvement~\cite{Mantyla2004,Yamashita2013,Sjoberg2013}. 
	As we show in this paper,  
	tools, text books, and developers disagree on what bad smells
	are important enough to hunt down and eliminate. Our findings
	are consistent with other research suggesting that universal bad
	smells that ignore project context are not useful to guide refactoring~\cite{Mantyla2004,Yamashita2013,Sjoberg2013}.

@@

	Two of the studies in \fig{smells} offers some comments on the relative importance
	of the different bad smells in the Yamashita'13 study and the developer study. Three of the bad smells listed in the top half of the Yamashita'13 rankings also score very high in the developer survey. Those three were {\em duplicated code, large class}, 
	and {\em long method}. 
	Note that this agreement also means that the
	Yamashita'13 study and the developer survey   
	believe
	that very few  code smells are   high priority issues
	requiring refactoring.

@@

	VARL encodes the defect count
	for each class as 0 (no defects known in class) or 1 (defects known in class).
	Univariate binary logistic regression is applied to learn three coefficients:  
	$\alpha$ is the intercept constant;
	$\beta$ is the coefficient for maximizing log-likelihood;
	and $p_0$ 
	measures   how well this  model predicts for  defects. A univariate logistic regression was conducted comparing metrics to defect counts. Any code metric with $p>0.05$ is ignored as being a poor defect predictor. Thresholds are then learned from the surviving metrics $M_c$ using
	an equation proposed by Bender:
	$$ \mathit{bad\; smell\; if\;} M_c > VARL$$
	\begin{equation}
		VARL = p^{-1}(p_0) =  \frac{1}{\beta }\left( {\log \left( {\frac{{{p_1}}}{{1 - {p_1}}}} \right) - \alpha } \right) 
	\end{equation}

@@

		{\bf RQ1: Effectiveness: } which of the methods defined in Section 3 is the best change oracle for identifying what and how code modules should be changed? 
		To   answer to this question, we will assume that developers
		refactor their code until the bad smell thresholds are not violated.
		This refactoring will start with some {\em initial} code
		base that is changed to a {\em new} code base. 
		For example, if the bad smell is \mbox{{\em loc $>100$}} and a 
		code module has 500 lines of code, we reason
		optimistically that we can change that code metric
		to 100.  
		Using the secondary verification oracle,  we then predict the
		number of defects in $d_+,d_-$ in {\em initial} and {\em new}. We evaluate the performance of XTREE, CD, Shatnawi, and Alves methods in setting bad smell thresholds.
		The best bad smell threshold method is the one that maximizes
		\begin{equation}\label{eq:diff}
			\mathit{improvement} = 100* \left(1 - \frac{ d_- }{ d_+}\right)
		\end{equation}

@@

		It can be difficult  to judge the  effects of removing bad smells.
		Refactored code cannot be assessed just by a rerun of the the test
		suite (since refactorings are supposed to preserve behavior). 
		% waiting to observe 
		% code refactorings is meant to
		% preserve the behavior of the system (i.e. the same tests
		% should pass before and after the refactoring). 
		Also, it many not be practical
		to assessing refactorings by making the
		refactorings,  then seeing what happens to that code for the rest
		of the project. In a test-driven agile project, as
		SCRUM meetings change what stories are implemented next,
		the operational profile that lead to defects in the old
		code may not be repeated in future executions.

		To resolve this  problem, SE researchers such as 
		Cheng et al.~\cite{Cheng10}, O'Keefe et al.~\cite{OKeeffe08,OKeeffe07},
		Moghadam~\cite{Moghadam2011} and Mkaouer et al.~\cite{Mkaouer14}
		use a {\em secondary verification oracle} (which is learned separately
		to the primary oracle) that   assesses
		how defective is the code before and after some
		refactoring. 
		For their second oracle,
		Cheng, O'Keefe, Moghadam and  Mkaouer et al. use the QMOOD hierarchical
		quality model~\cite{Bansiya02}.
		A shortcoming of QMOOD
		is that quality models learned from other projects
		may perform poorly when applied to new projects~\cite{localvsglobal}.
		Hence, for this study, we  eschew
		older quality models like QMOOD. Instead, we use
		Random Forests~\cite{Breiman2001} to learn defect predictors
		from OO code metrics.
		Note that, unlilke QMOOD, such measurements 
		are specific to the project, and the measurements can be reconstructed and the predictors rebuilt for other projects.

@@

		The {\bf RQ2} results showed that XTREE's recommendations are small in a {\em relative sense}; i.e. they are 
		relatively smaller than the other methods studied here.
		Note only that, but XTREE's recommendations are small in an {\em absolute sense}.
		Consider all frequency at which  \fig{counts} values for XTREE that are over 33\%; i.e. in at a third of our  repeated runs, XTREE mentioned
		a code attribute. For Ant, Ivy, Lucene, Jedit, and Poi, those frequencies
		are  \mbox{3, 3, 3, 4, 1, 2} respectively (out of twenty). This means that, usually, XTREE omits references to \mbox{17,17,17,16,19,18} static
		code attributes (out of 20). 
		Any refactoring based on a bad smell detector that uses  these omitted code attributes could hence  be stopped.

@@

		\fig{changes} also comments on the inter-relationships between static code attributes. Note that while some measures in
		\fig{changes} are decreased, many are increased.  
		For example, consider the {\em Poi} results
		from \fig{counts} that recommends decreasing {\em loc}
		but making large increases to {\em cbo} (coupling between
		objects). Here, XTREE is advising us to break up
		large classes class by into services
		in other classes. Note that such a refactoring will, by
		definition, increase the coupling between objects. 
		Note also that such increases  to reduce
		defects would never be proposed by the outlier methods
		of Shatnawi or Alves since their core assumption is that bad
		smells arise from unusually large code metrics.

@@

The results of this paper are biased by out choice of refactoring goal (reducing defects) and our choice
of measures collected from software project (OO measures such as
  depth of inheritance, number of child classes, etc).

@@

		\section{Conclusions}
		How to discourage useless refactorings?
		We say: ignore those not supported by the historical log of data from
		the current project.  
		When that data is not available (e.g. early
		in the project) then developers could use the general list of
		bad smells shown in \fig{smells}. However, 
		our results
		show that  bad smell detectors are most
		effective when they are based
		on a small handful of code metrics (as done by XTREE).
		Hence, using all the bad smells of \fig{smells} may not be optimal.

@@

			\item XTREE's conjunctions proved to be arguably as effective
			as those of Alves (see \fig{jur}) but far less verbose (see \fig{counts}). Since XTREE {\em approves} of fewer changes
			it hence {\em disapproves} of most changes. This makes it a better tool for critiquing and rejecting
			many of the refactorings.
		\end{itemize}
		Finally, XTREE does not suffer from the conjunctive fallacy.
		Older methods, such as those proposed by  Shatnawi and Alves assumed
		that the best way to improve code is to remove outlier  values. This may not work since when code is refactored,
		{\em the functionality has to go somewhere}. Hence,  reducing the lines of code in one module necessitates   
		{\em increasing} the coupling that module
		to other parts of the code. In future, we recommend software team use bad smell detectors that know what attribute measures
		need {\em decreasing} as well as {\em increasing}.

>>>>

		% \title{How to Discourage Useless Refactorings}
		\title{Recommendations For Intelligent Code Reorganization}

@@

		\begin{abstract} 
			{\bf Context: } 
			Developers use bad code smells to guide code reorganization.
			Yet developers, text books, tools, and researchers disagree on which bad smells are important.
			%Many bad smell detectors recommend refactoring when static code measure
			%cross some threshold boundary. 
			%%However, it is unclear at what threshold values smell-related metrics
			%should trigger code improvement or preventative maintenance.

			\noindent 
			{\bf Objective:} To evaluate the likelihood that a code reorganization to address bad code smells will yield improvement in the defect-proneness of the code.

@@

			\noindent
			{\bf Conclusion: }
			Before undertaking a code reorganization based on a bad smell report,
			use a tool like XTREE to check and ignore any code reorganizations   that  are useless; i.e. which lacks evidence
			in the historical record  that it is useful to make that change.
			Note that this use case applies to both manual code reorganizations proposed by developers
			as well as refactoring  conducted by automatic methods.
			This recommendation assumes that there is an historical record.
			If none exists, then the results of this paper could be use used as a guide (see our
			Table~8).

@@

	Bad smells are a widely used technique for evaluating code. While the original bad small concept was largely subjective~\cite{fowler99}, researchers including Marinescu~\cite{marinescu06} and others has provided formal definitions of ``bad smells'' in terms of static code attributes such size, complexity, coupling, and other metrics. Consequently, code smells are captured by popular static analysis tools such as PMD\footnote{https://github.com/pmd/pmd}, CheckStyle\footnote{http://checkstyle.sourceforge.net/}, FindBugs\footnote{http://findbugs.sourceforge.net/}, and SonarQube\footnote{http://www.sonarqube.org/}, although not always explicitly labeled as such.

	Refactoring bad smells from code is generally accepted as a recommended practice, but code reorganization by definition does not change the external functionality of the system and thus may have no perceived value. For example, this paper began when a Washington-based software company shared one of their management challenges with us: their  releases are delayed by developers spending  much time removing bad smells within their code. 
	%This management team wanted some way to check if all that activity was useful. 
	Kim et al.\cite{kim2012field} surveyed developers at Microsoft and found that refactoring incurs significant cost and risks. A Google search on the terms ``refactoring cost'' yields numerous threads on StackOverlfow from developers asking how to justify refactoring and when the costs of refactoring outweight its benefits.

@@

	% In addition to tools that capture bad smells such as FindBugs and SonarQube, a multitude of tools have been proposed to support refactoring (e.g., \cite{ge2014manual,lee2013drag,foster2012witchdoctor,ge2012reconciling}). Note that these managers are {\em not} asking for better
	% automatic refactoring
	% tool support. 
	% Their human programmers are refactoring
	% code all the time, perhaps too much so.
	% Hence, the management goal
	The challenge is to encourage code reorganizations that result in perceivable benefits (such as reduced defect proneness or lower maintenance costs) and avoid code reorganizations with no demonstrable benefit and thus waste effort.

	This paper describes one approach to evaluate whether code reorganizations that change the structure of code are likely to have a perceivable benefit by evaluating:
	\bi
	\item If there is no evidence in the historical record that changing ``X'' is useful;
	\item Then discourage developers from doing ``X''.
	\ei
	We use data mining to generate two oracles: a {\em primary
		change oracle} and a {\em secondary verification oracle}.
	By combining these two oracles,
	we can generate and validate useful
	changes to code modules. We focus on ``bad smells'' indicated by code metrics such as size and complexity as captured in popular tools such as SonarQube and Klocwerk [REF].

@@

	When these oracles were applied to defect data from
	open source object-oriented software systems, we discovered a {\em conjunctive fallacy}
	in the bad smell literature~\cite{erni96,bender99,Shatnawi10,Alves2010,hermans15}.
	A common heuristic is to recommend code reorganization of ``bad'' code
	to make it ``better'' as follows: for all static code measures that exceed some threshold, make changes such that the thresholds are no longer exceeded. That is:
	\begin{equation}\label{eq:df}
		\scriptstyle
		\begin{array}{rl}
			\mathit{bad}    & = \left(a_1 > t_1 \right) \bigvee \left(a_2 > t_2\right) \bigvee    ...                             \\
			\mathit{better} & = \neg\;\mathit{bad} = \left(a_1 \le t_1 \right) \bigwedge \left(a_2 \le t_2\right)  \bigwedge  ... 
		\end{array}
	\end{equation}
	We say that the above definition of ``better'' is a conjunctive fallacy
	since it assumes that the best way to improve code is to decreases multiple code attribute measures below $t_i$ in order
	to remove the ``bad'' smells. In reality, there exists an intricate set of associations between static code measures
	such that {\em decreasing}  $a_i$ necessitates {\em increasing} $a_j$.
	It is easy to see why this is so.
	A requirement for  code reorganization is that the new code supports the same functionality
	as before. If we pull code out of a function (since that function has grown too
	large), {\em that functionality has to go somewhere else}. What we see in XTREE's change
	recommendation is that if we decrease a module's lines of code  then in the refactored
	code, the functionality is achieved via a communication between several different parts
	of the system. That is, {\em decreasing} the lines of code metric within a module {\em increases}
	that module's coupling metrics.

@@

	This paper  claims that (a)~XTREE is a  better way than \eq{df}  to define useful changes to software and (b)~those changes are useful for recognizing   superfluous code reorganizations since they usually refer to a very 
	small subset of the static code measures (which allows us to rule out code reorganizations based on any of the omitted
	static code measures). 
	In support of these claims, 
	the rest of this paper is structured as follows. In Section~2, we offer some background on bad smells. In Section~3, 
	different methods are presented for determining when code does/does not have bad smell. One of those methods
	will be XTREE while the others will come from other researchers. Section~4
	defines an assessment method that checks which of these methods is most useful. The results from that assessment 
	are presented in Section~5. Those results will answer five research questions.

@@

	{\bf RQ3: Stopping}: Our advice to managers is to discourage code reorganization based on changes that lack
	historical evidence of being effective. How effective is XTREE at offering such ``stopping points'' (i.e. clear guidance on what {\em not} to do)??
	\begin{lesson}
		In  any  project,  XTREE's  recommended  changes  only  mentions one to four 
		of the  static code attributes.  Any bad smell defined in terms of the remaining 19 to 16 code attributes (i.e. most of them)
		would hence be deprecated.
	\end{lesson}

@@

	{\bf RQ5: Conjunctive Fallacy}:  
	Is it always  useful  to aplly \eq{df}; i.e. make code better by   reducing the values of  multiple code attributes? We find that:
	\begin{lesson}
		XTREE usually recommends reducing lines of code (size of the modules).
		That said,  XTREE often recommends {\em increasing} the values of other static code attributes.
	\end{lesson} 
	Note that {\bf RQ3, RQ4, RQ5} 
	confirms the intuitions
	of the project managers that prompted this investigation:
	\bi
	\item
	Yes,  indeed, their programmers
	were wasting time on   performing code reorganizations  that  decreased multiple measures when, in fact,
	they should be trying to {\em decrease} some measures while {\em increasing} others.
	\item
	Across all studied projects, XTREE found that  around one-fifth  
	of the measures were usually found within  change recommendations. That is, it is 80\% likely that
	that code reorganization based on reducing any one measurement picked at random will be useful.
	\ei
	Consequently, we  recommend the following use case for  XTREE:
	\bi
	\item Before doing  code reorganization based on a bad smell report...
	\item ...check and discourage any code reorganization   for which there is no proof
	in the historical record that the change improves the code.
	\ei
	This use case described  applies to both manual code reorganizations proposed by developers
	as well as refactoring conducted by automatic methods~\cite{mkaouer2015many}. That is, XTREE could optimize automatic
	code refactoring by discouraging refactorings for useless goals.

@@

	Much research endorses them to guide
	code improvement (e.g., code reorganization or preventative maintenance). A recent literature review by Tufano et al.~\cite{Tufano2015}  
	lists dozens of papers on smell detection and repair tools. 
	Yet
	other papers cast doubt on the value of bad smells
	as triggers for code improvement~\cite{Mantyla2004,Yamashita2013,Sjoberg2013}. 
	As we show in this paper,  
	tools, text books, and developers disagree on what bad smells
	are important enough to hunt down and eliminate. Our findings
	are consistent with other research suggesting that universal bad
	smells that ignore project context are not useful to guide refactoring~\cite{Mantyla2004,Yamashita2013,Sjoberg2013}.

@@

	Two of the studies in \fig{smells} offers some comments on the relative importance
	of the different bad smells in the Yamashita'13 study and the developer study. Three of the bad smells listed in the top half of the Yamashita'13 rankings also score very high in the developer survey. Those three were {\em duplicated code, large class}, 
	and {\em long method}. 
	Note that this agreement also means that the
	Yamashita'13 study and the developer survey   
	believe
	that very few  code smells are   high priority issues
	requiring code reorganization.

@@

	VARL encodes the defect count
	for each class as 0 (no defects known in class) or 1 (defects known in class).
	Univariate binary logistic regression is applied to learn three coefficients:  
	$\alpha$ is the intercept constant;
	$\beta$ is the coefficient for maximizing log-likelihood;
	and $p_0$ 
	measures   how well this  model predicts for  defects. A univariate logistic regression was conducted comparing metrics to defect counts. Any code metric with $p>0.05$ is ignored as being a poor defect predictor. Thresholds are then learned from the surviving metrics $M_c$ using
	an equation proposed by Bender:
	$$ \mathit{bad\; smell\; if\;} M_c > VARL$$
	Where,
	\begin{equation}
		VARL = p^{-1}(p_0) =  \frac{1}{\beta }\left( {\log \left( {\frac{{{p_1}}}{{1 - {p_1}}}} \right) - \alpha } \right) 
	\end{equation}

@@

		{\bf RQ1: Effectiveness: } which of the methods defined in Section 3 is the best change oracle for identifying what and how code modules should be changed? 
		To   answer to this question, we will assume that developers
		refactor their code until the bad smell thresholds are not violated.
		This code reorganization will start with some {\em initial} code
		base that is changed to a {\em new} code base. 
		For example, if the bad smell is \mbox{{\em loc $>100$}} and a 
		code module has 500 lines of code, we reason
		optimistically that we can change that code metric
		to 100.  
		Using the secondary verification oracle,  we then predict the
		number of defects in $d_+,d_-$ in {\em initial} and {\em new}. We evaluate the performance of XTREE, CD, Shatnawi, and Alves methods in setting bad smell thresholds.
		The best bad smell threshold method is the one that maximizes
		\begin{equation}\label{eq:diff}
			\mathit{improvement} = 100* \left(1 - \frac{ d_- }{ d_+}\right)
		\end{equation}

@@

		It can be difficult  to judge the  effects of removing bad smells.
		Refactored code cannot be assessed just by a rerun of the the test
		suite (since refactorings are supposed to preserve behavior). 
		% waiting to observe 
		% code refactorings is meant to
		% preserve the behavior of the system (i.e. the same tests
		% should pass before and after the refactoring). 
		Also, it many not be practical
		to assessing code reorganizations by making the
		code reorganizations,  then seeing what happens to that code for the rest
		of the project. In a test-driven agile project, as
		SCRUM meetings change what stories are implemented next,
		the operational profile that lead to defects in the old
		code may not be repeated in future executions.

		To resolve this  problem, SE researchers such as 
		Cheng et al.~\cite{Cheng10}, O'Keefe et al.~\cite{OKeeffe08,OKeeffe07},
		Moghadam~\cite{Moghadam2011} and Mkaouer et al.~\cite{Mkaouer14}
		use a {\em secondary verification oracle} (which is learned separately
		to the primary oracle) that   assesses
		how defective is the code before and after some
		code reorganization. 
		For their second oracle,
		Cheng, O'Keefe, Moghadam and  Mkaouer et al. use the QMOOD hierarchical
		quality model~\cite{Bansiya02}.
		A shortcoming of QMOOD
		is that quality models learned from other projects
		may perform poorly when applied to new projects~\cite{localvsglobal}.
		Hence, for this study, we  eschew
		older quality models like QMOOD. Instead, we use
		Random Forests~\cite{Breiman2001} to learn defect predictors
		from OO code metrics.
		Note that, unlilke QMOOD, such measurements 
		are specific to the project, and the measurements can be reconstructed and the predictors rebuilt for other projects.

@@

		The {\bf RQ2} results showed that XTREE's recommendations are small in a {\em relative sense}; i.e. they are 
		relatively smaller than the other methods studied here.
		Note only that, but XTREE's recommendations are small in an {\em absolute sense}.
		Consider all frequency at which  \fig{counts} values for XTREE that are over 33\%; i.e. in at a third of our  repeated runs, XTREE mentioned
		a code attribute. For Ant, Ivy, Lucene, Jedit, and Poi, those frequencies
		are  \mbox{3, 3, 3, 4, 1, 2} respectively (out of twenty). This means that, usually, XTREE omits references to \mbox{17,17,17,16,19,18} static
		code attributes (out of 20). 
		Any code reorganization based on a bad smell detector that uses  these omitted code attributes could hence  be stopped.

@@

		\fig{changes} also comments on the inter-relationships between static code attributes. Note that while some measures in
		\fig{changes} are decreased, many are increased.  
		For example, consider the {\em Poi} results
		from \fig{counts} that recommends decreasing {\em loc}
		but making large increases to {\em cbo} (coupling between
		objects). Here, XTREE is advising us to break up
		large classes class by into services
		in other classes. Note that such a code reorganization will, by
		definition, increase the coupling between objects. 
		Note also that such increases  to reduce
		defects would never be proposed by the outlier methods
		of Shatnawi or Alves since their core assumption is that bad
		smells arise from unusually large code metrics.

@@

The results of this paper are biased by our choice of code reorganization goal (reducing defects) and our choice
of measures collected from software project (OO measures such as
  depth of inheritance, number of child classes, etc).

@@

		\section{Conclusions}
		How to discourage useless code reorganizations?
		We say: ignore those not supported by the historical log of data from
		the current project.  
		When that data is not available (e.g. early
		in the project) then developers could use the general list of
		bad smells shown in \fig{smells}. However, 
		our results
		show that  bad smell detectors are most
		effective when they are based
		on a small handful of code metrics (as done by XTREE).
		Hence, using all the bad smells of \fig{smells} may not be optimal.

@@

			\item XTREE's conjunctions proved to be arguably as effective
			as those of Alves (see \fig{jur}) but far less verbose (see \fig{counts}). Since XTREE {\em approves} of fewer changes
			it hence {\em disapproves} of most changes. This makes it a better tool for critiquing and rejecting
			many of the code reorganizations.
		\end{itemize}
		Finally, XTREE does not suffer from the conjunctive fallacy.
		Older methods, such as those proposed by  Shatnawi and Alves assumed
		that the best way to improve code is to remove outlier  values. This may not work since when code is refactored,
		{\em the functionality has to go somewhere}. Hence,  reducing the lines of code in one module necessitates   
		{\em increasing} the coupling that module
		to other parts of the code. In future, we recommend software team use bad smell detectors that know what attribute measures
		need {\em decreasing} as well as {\em increasing}.
